### 2025-02-16 paper/sections/method.qmd
nearly there here

$$
\text{div}(\mathbf{x},\mathbf{x^\prime},y;\theta) = \mathcal{E}_\theta(\mathbf{x},y) - \mathcal{E}_\theta(\mathbf{x}^\prime,y)
$$ {#eq-div}

where $\mathcal{E}_\theta(\cdot)$ denotes the energy function. We generate samples $\mathbf{x}^\prime$ by first randomly sampling the target class $y^+ \sim p(y)$ and then generating a counterfactual explanation for that target, similar to how conditional sampling is used to draw from $p_\theta(\mathbf{x})$ in @grathwohl2020your. In particular, we set $\mathcal{E}_\theta(\mathbf{x},\mathbf{y})=-\mathbf{M}_\theta(\mathbf{x})[y^+]$ where $y^+$ denotes the index of the target class.

@@

$$
\begin{aligned}
\text{advloss}(\mathbf{M}_\theta(\mathbf{x^\prime}),\mathbf{y};\varepsilon)&=\begin{cases}
\text{yloss}(\mathbf{M}_\theta(\mathbf{x^\prime}),\mathbf{y}) & \text{if} \ ||\Delta||_\infty \leq \varepsilon \\
0 & \text{otherwise.}
\end{cases}
\end{aligned}
$$ {#eq-adv}

>>>>

$$
\text{div}(\mathbf{x},\mathbf{x}_T^\prime,y;\theta) = \mathcal{E}_\theta(\mathbf{x},y) - \mathcal{E}_\theta(\mathbf{x}_T^\prime,y)
$$ {#eq-div}

where $\mathcal{E}_\theta(\cdot)$ denotes the energy function. In particular, we set $\mathcal{E}_\theta(\mathbf{x},\mathbf{y})=-\mathbf{M}_\theta(\mathbf{x})[y^+]$ where $y^+$ denotes the index of the target class. We generate samples $\mathbf{x}_T^\prime$ by first randomly sampling the target class $y^+ \sim p(y)$ and then generating a counterfactual explanation for that target over $T$ iterations using a gradient-based counterfactual generator. This is similar to how conditional sampling is used to draw from $p_\theta(\mathbf{x})$ in @grathwohl2020your.

@@

$$
\begin{aligned}
\text{advloss}(\mathbf{M}_\theta(\mathbf{x}_{t\leq T}^\prime),\mathbf{y};\varepsilon)&=\text{yloss}(\mathbf{M}_\theta(\mathbf{x}_{t_\varepsilon}^\prime),\mathbf{y}) \\
t_\varepsilon &= \max_t \{t: ||\Delta||_\infty < \varepsilon\}
\end{aligned}
$$ {#eq-adv}
